E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-11 introduction.tex
slight formatting changes done
prelim edit chap1

	The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the Web has made it possible for the general public to access it anywhere and on multiple devices like phones, laptops, personal digital assistants, and even on TVs and cars. This has ushered in an era of responsive web applications which depend on user input. While this rapid pace of development has improved the speed of dissemination of information, it does come at a cost. Attackers have an added incentive to break into user's e-mail accounts more than ever. E-Mail accounts are usually connected to almost all other online accounts of a user, and e-mails continue to serve as the principal mode of official communication on the web for most institutions. Thus, the impact an attacker can have by having control over the e-mail communication sent by websites to users is of an enormous magnitude.

@@

\subsection*{Structure of document} % describes the remaining sections and gives a short desc about them
This thesis document is divided logically into the following sections:
\begin{itemize}
	\item Chapter 2 discusses the background of E-Mail Header Injection, a brief history of the vulnerability, and enumerates the languages and platforms affected by this vulnerability.

	\item Chapter 3 discusses the System design, the architecture, and the components of the system.

	\item Chapter 4 describes the experimental setup and sheds light on how we overcame the issues and assumptions discussed in Chapter 3.

	\item Chapter 5 presents our findings and our analysis of the results.

	\item Chapter 6 continues the discussion of the results; the lessons learned over the course of the project, limitations, and a suitable mitigation strategy to overcome the vulnerability.

	\item Chapter 7 explores related work in the area.

	\item Chapter 8 concludes this thesis, with ideas to expand the research in this area.
\end{itemize}

>>>>

\section{Introduction}
	The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the Web has made it possible for the general public to access it anywhere and on multiple devices like phones, laptops, personal digital assistants, and even on TVs and cars. This has ushered in an era of responsive web applications which depend on user input. While this rapid pace of development has improved the speed of dissemination of information, it does come at a cost. Attackers have an added incentive to break into user's e-mail accounts more than ever. E-Mail accounts are usually connected to almost all other online accounts of a user, and e-mails continue to serve as the principal mode of official communication on the web for most institutions. Thus, the impact an attacker can have by having control over the e-mail communication sent by websites to users is of an enormous magnitude.

@@
